A Java Framework For Embarrassingly Parallel Problems

### 2013-12-11 paper/paper.tex
more paper stuff

\documentclass[12pt]{article} 
\usepackage{graphics}
\usepackage{setspace}
\usepackage{cite}
\usepackage{wrapfig}

@@

\begin{wrapfigure}{R}{0.5\textwidth}
    \begin{center}
        \includegraphics{figures/ep.jpg}
    \end{center}
    \caption{Embarrassingly Parallel Model}
    \label{fig:ep}
\end{wrapfigure}

@@

@@

\begin{wrapfigure}{L}{0.5\textwidth}
    \begin{center}
        \includegraphics{figures/MapReduce.jpg}
    \end{center}
    \caption{MapReduce Model}
    \label{fig:map}
\end{wrapfigure}

\section{Proposed Solution}
\begin{figure}
{\resizebox{5.2in}{!}{\includegraphics{figures/uml.png}}}
\caption{UML for the embarrassingly parallel framework}
\label{fig:uml}
\end{figure}
The only requirements for a program to be wrapped by framework are that it 
process the input in an embarrassingly parallel manner and that the input comes 
from a file. The processed results must also written to a file. The framework 
supports two forms of input: a directory of files that contain that each contain
one unit of work, which is represented by the Chunk class, or a single file that
the framework can break up into Chunks. For example, the Ka/Ks Calculator's 
input consists of a header and then two protein sequence lines followed by a 
blank line. The framework uses that blank line to know when one Chunk of work 
has ended and another has begun. The user can input a regular expression to 
define when lines of input are separated into Chunks. This occurs in the 
ChunkManager class.

@@

\begin{figure}
{\resizebox{5.2in}{!}{\includegraphics{experiment/out.png}}}
\caption{Runtimes for the Ka/Ks Calculator though the framework}
\label{fig:kaksgraph}
\end{figure}

@@

A version of octupus was also run through the framework and was tested against
two different sized data sets. Both sets were first clustered at 90\%, 95\% and
97\% minimum similarity. The runtime for those tests can be seen in table
\ref{tab:oct1}. The resulting clusters from the 90\% similarity run were used as
the input for the framework's runs, which were all set for 97\% similarity. 
The framework in this case was just run at six, eight and ten workers. Table 
\ref{tab:octu2} shows that it is slightly faster to cluster first at 90\% and 
then run the resulting clusters through the framework at a higher similarity.

\begin{table}
    \begin{tabular}{|l|l|l|}
        \hline
        Number of Sequences & Minimum Similarity & Time(s) \\ \hline
        1500                & 90\%               & 99      \\
        ~                   & 95\%               & 115     \\
        ~                   & 97\%               & 131     \\ \hline
        6500                & 90\%               & 425     \\
        ~                   & 95\%               & 496     \\
        ~                   & 97\%               & 603     \\ \hline
    \end{tabular}
    \label{tab:octu1}
\end{table}

\begin{table}
    \begin{tabular}{|l|l|l|}
        \hline
        Number of Sequences & Number of Workers & Time(s) \\ \hline
        1500                & 6                 & 34      \\
        ~                   & 8                 & 27      \\
        ~                   & 10                & 27      \\ \hline
        6500                & 6                 & 127     \\
        ~                   & 8                 & 127     \\
        ~                   & 10                & 123     \\ \hline
    \end{tabular}
    \label{tab:octu2}
\end{table}

>>>>

\documentclass[12pt]{article} 
\usepackage{graphics}
\usepackage{setspace}
\usepackage{cite}
\usepackage{floatrow}

@@

\begin{figure}
    \begin{center}
        \includegraphics{figures/ep.jpg}
    \end{center}
    \caption{Embarrassingly Parallel Model}
    \floatfoot{http://www.coopsoft.com/ar/i/fjGraph.jpg}
    \label{fig:ep}
\end{figure}

@@

\begin{figure}
    \begin{center}
        \resizebox{4.7in}{!}{\includegraphics{figures/MapReduce.jpg}}
    \end{center}
    \caption{MapReduce Model}
    \label{fig:map}
    \floatfoot{http://dme.rwth-aachen.de/en/system/files/file\_upload/project/MapReduce.jpg}
\end{figure}

@@

\section{Proposed Solution}
\begin{figure}
    \begin{center}
        \resizebox{4.7in}{!}{\includegraphics{figures/uml.png}}
    \end{center}
    \caption{UML for the embarrassingly parallel framework}
    \label{fig:uml}
\end{figure}

The only requirements for a program to be wrapped by framework are that it 
process the input in an embarrassingly parallel manner and that the input comes 
from a file. The processed results must also written to a file. The framework 
supports two forms of input: a directory of files that contain that each contain
one unit of work, which is represented by the Chunk class, or a single file that
the framework can break up into Chunks. For example, the Ka/Ks Calculator's 
input consists of a header and then two protein sequence lines followed by a 
blank line. The framework uses that blank line to know when one Chunk of work 
has ended and another has begun. The user can input a regular expression to 
define when lines of input are separated into Chunks. This occurs in the 
ChunkManager class.

@@

\begin{figure}
    \begin{center}
        \resizebox{5.2in}{!}{\includegraphics{experiment/time.png}}
    \end{center}
    \caption{Runtimes for the Ka/Ks Calculator though the framework}
    \label{fig:kaksgraph}
\end{figure}

@@

A version of octupus was also run through the framework and was tested against
two different sized data sets. Both sets were first clustered at 90\%, 95\% and
97\% minimum similarity. The runtime for those tests can be seen in table
\ref{tab:octu1}. The resulting clusters from the 90\% similarity run were used as
the input for the framework's runs, which were all set for 97\% similarity. 
The framework in this case was just run at six, eight and ten workers. Table 
\ref{tab:octu2} shows that it is slightly faster to cluster first at 90\% and 
then run the resulting clusters through the framework at a higher similarity.

\begin{table}
    \begin{center}
    \begin{tabular}{|l|l|l|}
    \hline
        Number of Sequences & Minimum Similarity & Time(s) \\ \hline
        1500                & 90\%               & 99      \\
        ~                   & 95\%               & 115     \\
        ~                   & 97\%               & 131     \\ \hline
        6500                & 90\%               & 425     \\
        ~                   & 95\%               & 496     \\
        ~                   & 97\%               & 603     \\ \hline
    \end{tabular}
    \caption{Times from serial octupus at various similarity levels.}
    \end{center}
    \label{tab:octu1}
\end{table}

\begin{table}
    \begin{center}
    \begin{tabular}{|l|l|l|}
        \hline
        Number of Sequences & Number of Workers & Time(s) \\ \hline
        1500                & 6                 & 34      \\
        ~                   & 8                 & 27      \\
        ~                   & 10                & 27      \\ \hline
        6500                & 6                 & 127     \\
        ~                   & 8                 & 127     \\
        ~                   & 10                & 123     \\ \hline
    \end{tabular}
    \caption{Times from octupus through the framework at 97\% similarirty.}
    \end{center}
    \label{tab:octu2}
\end{table}
